Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-09 exp1/present2013.tex
about benchmarks
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@659 43ef1190-90fd-4dd7-a769-d0121f02b80e
use descripiton instead of itemize
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@660 43ef1190-90fd-4dd7-a769-d0121f02b80e
show notes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@661 43ef1190-90fd-4dd7-a769-d0121f02b80e

%\documentclass[english,aspectratio=169]]{ifislide}
%\documentclass[english,print,aspectratio=169]{ifislide}
\documentclass[english,handout,aspectratio=169]{ifislide}
\usepackage{verbatim}
\usepackage{wrapfig}

\usepackage[utf8]{inputenc}
% Packages used specific for this lecture:

@@

\begin{frame}{What's a benchmark?}
\end{frame}
\note{If your queries are all fully known, by all means, run them}
\note{In most scientific relevant cases, no such assumptions can be
  made}

@@

\begin{frame}{Factors and levels}
  \begin{itemize}
  \item [``Implement''] The implementation under evaluation.
  \item [``TripleC''] 1 or 2 MTriples from the DBPedia SPARQL
    Benchmark.
  \item [``Machine''] Software and hardware platform, one smaller
    machine with fast SSD and one larger with slower disks in RAID1.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]{The Basic Graph pattern factor}
  \begin{itemize}

@@

@@

\begin{frame}[fragile]{Absence or presence factors}
  \begin{itemize}
  \item [``Union''] Absence or presence of a \textsf{UNION} pattern.

@@

  \end{itemize}
\end{frame}
\note{Implemented in R, using packages \texttt{DoE.base} and \texttt{FrF2}.}
\note{Two experiment machines, one machine running queries}
\note{No warm-up, no cache busting}
\note{256 experiments in full factorial, no replications, compare
  favorably to benchmarks}

@@

\end{frame}
\note{The paper shows how similar testing can be done to investigate
  when the new implementation fails.} % TODO: Add more on this?

>>>>

%\documentclass[english,aspectratio=196]]{ifislide}
%\documentclass[english,print,aspectratio=169]{ifislide}
\documentclass[english,handout,aspectratio=169]{ifislide}
\usepackage{verbatim}
\usepackage{wrapfig}
\setbeameroption{show notes}
\usepackage[utf8]{inputenc}
% Packages used specific for this lecture:

@@

\begin{frame}{What's a benchmark?}

  \begin{itemize}
  \item Natural benchmarks.
  \item Benchmarking with broad and well-known workloads. 
  \item Use-case driven benchmarks.
  \end{itemize}

\end{frame}
\note{Natural benchmarks, query log-derived, DBPedia SPARQL Benchmark}
\note{If your queries are all fully known, by all means, run them}
\note{In most scientific relevant cases, no such assumptions can be
  made}
\note{What I will present will likely create artifical workloads}
\note{Use-case driven will seem artificial for everything else}

@@

\begin{frame}{Factors and levels}
  \begin{description}
  \item [``Implement''] The implementation under evaluation.
  \item [``TripleC''] 1 or 2 MTriples from the DBPedia SPARQL
    Benchmark.
  \item [``Machine''] Software and hardware platform, one smaller
    machine with fast SSD and one larger with slower disks in RAID1.
  \end{description}
\end{frame}

\begin{frame}[fragile]{The Basic Graph pattern factor}
  \begin{description}

@@

  \end{description}

@@

\begin{frame}[fragile]{Absence or presence factors}
  \begin{description}
  \item [``Union''] Absence or presence of a \textsf{UNION} pattern.

@@

  \end{description}
\end{frame}
\note{Implemented in R, using packages \texttt{DoE.base} and \texttt{FrF2}.}
\note{Two experiment machines, one machine running queries}
\note{No warm-up, no cache busting}
\note{256 experiments in full factorial, no replications, compare
  favorably to benchmarks}

@@

\end{frame}
\note{The paper shows how similar testing can be done to investigate
  when the new implementation fails.}
